Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2022-02-11 Manuscript/Imputation_of_Incomplete_Multilevel_Data.Rmd
Clean-up and rename manuscript file

---
documentclass: jss
author:
  - name: Hanne Oberman
    affiliation: Utrecht University
    address: |
      | Padualaan 14
      | 3584 CH Utrecht
    email: \email{h.i.oberman@uu.nl}
    url: https://hanneoberman.github.io/
  - name: Johanna Mu\~noz Avila
    affiliation: University Medical Center Utrecht \AND
  - name: Valentijn de Jong
    affiliation: University Medical Center Utrecht 
  - name: Gerko Vink
    affiliation: Utrecht University \AND
  - name: Thomas Debray
    affiliation: University Medical Center Utrecht 
title:
  formatted: "Imputation of Incomplete Multilevel Data with \\pkg{mice}"
  plain:     "Imputation of Incomplete Multilevel Data with mice"
  short:     "Multilevel \\pkg{mice}"
abstract: >
  This is a tutorial paper on imputing incomplete multilevel data with \pkg{mice}. Footnotes in the current version show work in progress/under construction. The last section is not part of the manuscript, but purely for reminders.
keywords:
  # at least one keyword must be supplied
  formatted: [missing data, multilevel, clustering, "\\pkg{mice}", "\\proglang{R}"]
  plain:     [missing data, multilevel, clustering, mice, R]
preamble: >
  \usepackage{amsmath}
header-includes: 
 - \usepackage{graphicx} 
 - \usepackage{mathtools}
 - \usepackage{ulem}
output: rticles::jss_article
bibliography: ../References/multilevelmice.bib
editor_options: 
  chunk_output_type: inline
---

@@

```{r patterns, fig.height=3, fig.width=4.1, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
# TODO: make cluster part f the data (blue)
# TODO: dots between 2 and N, for each variable
```

@@

<!-- While the sporadic missingness in $X1$ would at least provide some information for each cluster. can be further subdivided depending on the underlying true value of the missing entries: this can either be  constant within clusters, or a non-measured random variable (which may differ per unit within clusters). In Figure 1, the former would imply that the unobserved values for units 3 and 4 on column $X2$ are identical. With the latter, the values would differ. The pattern of the missing data across clusters determines the optimal strategy for dealing with the missingness. -->

Ignoring the missingness in analyses can be extremely harmful to inferences. Complete case analysis can introduce bias in statistical inferences and lowers statistical power. Instead, the missingness should be accommodated \emph{before} or _within_ the analysis of scientific interest. Especially the former is very generic and popular. Imputing (i.e., filling in) the missing values separates the missing data problem from the scientific problem: missing data are replaced by plausible values whereafter the completed data is analysed as if it were completely observed. The \proglang{R} package \pkg{mice} has become the de-facto standard for imputation by chained equations, which iteratively solves the missingness on a variable-by-variable basis. \pkg{mice} is known to yield valid inferences under many different missing data circumstances [@buur18]. In this paper, we will discuss how to use \pkg{mice} in the context of multilevel data.

<!-- "We find it useful to distinguish the missingness pattern, which describes which values are missing and observed in the data matrix and the missingness mechanism (or mechanisms), which concerns the relationship between missingness and the values of variables in the data matrix" (Little and Rubin, p. 8). -->

<!-- Another characteristic of the missing data to take into account in analyses is the mechanism behind the missingness. Although the essence of the true non-response mechanism may not be known, it can be inferred or assumed to be one of the following: -->

<!-- - Missing Completely At Random (MCAR), where the probability to be missing is equal across all data entries; -->
<!-- - Missing At Random (MAR), where the probability to be missing depends on observed information; -->
<!-- - Missing Not At Random (MNAR), where the probability to be missing depends on unrecorded information, making the missingness non-ignorable [@rubi76; @meng94]. -->
<!-- Depending on the assumed missingness mechanism, missing data handling strategies may be more or less suitable, see e.g., @yuce08 and @hox15. -->

@@

For each of these datasets, we will discuss the nature of the missingness, choose one or more imputation models and evaluate the imputed data, but we will also highlight one specific asect of the imputation workflow. With the `popmis` data, we show how (not) to develop an imputation model. With the `hiv` data we focus on extending the imputation model to include Heckman-type selection-inclusion methods. And with the `impact` data we provide a example of multivariate missingness in real-world data. Together, this should give enough scaffolding for applied researchers who are faced with incomplete multilevel data.

@@

```{r pop, echo=FALSE, message=FALSE, warning=FALSE}
# randomly select a few classes
# clusters <- sample(1:100, 10)

# load data 
# popmis <- mice::popmis 
#readRDS("../Data/popNCR2.RDS") %>% 
  #filter(class %in% clusters) %>% 
  #mutate(class = as.factor(class))
# popcomp <- foreign::read.spss("../Data/popular.sav", to.data.frame = TRUE, use.value.labels = FALSE) %>% 
#   mutate(school = SCHOOL,
#          popular = POPULAR,
#          sex = SEX,
#          texp = TEXP,
#          .keep = "none")
est_comp <- lme4::lmer(popular ~ 1 + sex + texp + sex:texp + (1 + sex | school), popcomp) 
# %>% 
#   broom.mixed::tidy(conf.int = TRUE) 
# %>% 
  # mutate(
  #   term = factor(term, levels = c("(Intercept)", "sex", "texp", "sex:texp", "sd__(Intercept)", "cor__(Intercept).sex", "sd__sex", "sd__Observation"), labels = c("Intercept", "Sex", "Teacher experience", "Cross-level interaction", "SD cluster-level residual error", "Cor. cluster-level error and slopes sex", "SD residual slopes sex", "SD unit-level residual error"), ordered = TRUE))
```

@@

<!-- TODO: add all estimimates, seed, and version nr., this also shows the workflow for pooling etc. -->

@@

```{r echo=FALSE}
# lvl <- c("(Intercept)", "sex", "texp", "sex:texp", "sd__(Intercept)", "cor__(Intercept).sex", "sd__sex", "sd__Observation")
# lbl = c("Intercept", "Sex", "Teacher experience", "Cross-level interaction", "SD cluster-level residual error", "Cor. cluster-level error and slopes sex", "SD residual slopes sex", "SD unit-level residual error")
est_comp %>% 
  broom.mixed::tidy("fixed", conf.int = TRUE) %>% 
  mutate(term = term,
         estimate  = paste0(
           round3(estimate), " [", 
           round3(conf.low), ", ", 
           round3(conf.high), "]"), 
         .keep = "none")

# est_comp %>% 
#   broom.mixed::tidy("ran_pars") %>% 
#   mutate(term = term, #factor(term, levels = unique(.$term), labels = c()),
#          estimate  = round3(estimate), 
#          .keep = "none")
```

<!--  Let's apply the following five methods: -->

<!-- sample: Find imputations by random sampling from the observed values in lpo. This method ignores sch; -->

<!-- pmm: Single-level predictive mean matching with the school indicator coded as a dummy variable; -->

<!-- 2l.pan: Multilevel method using the linear mixed model to draw univariate imputations; -->

<!-- 2l.norm: Multilevel method using the linear mixed model with heterogeneous error variances; -->

<!-- 2l.pmm: Predictive mean matching based on predictions from the linear mixed model, with random draws from the regression coefficients and the random effects, using five donors. -->

@@

```{r pop_pat, echo=FALSE, fig.cap = "Missing data pattern in the popularity data", message=FALSE, warning=FALSE}
# missingness
plot_md_pat(popmis)
# TODO: add pattern by cluster, text mining example square size
# TODO: try to make it a shepley plot

# popcomp <- popcomp %>% 
#   cbind(R = is.na(popmis$popular))
# t.test(x = popcomp$popular[popcomp$R], y = popcomp$popular[!popcomp$R]) 
# ggplot(popcomp, aes(y=popular, x = R)) +
#   geom_boxplot()

@@

In Figure \ref{fig:pop_dist} we see that **[update this part]** the distribution for the missing `popular` is further to the right than the distribution for observed `popular`. This would indicate a right-tailed MAR missingness. (In fact, this is exactly what happens, because the missingness in these data was created manually.) We've made it observable by examining the relations between the missingness in popular and the observed data in `texp`. 
<!-- There is also a dependency between the missingness in teacher popularity and pupil popularity. The relation seems to be right-tailed as well. -->

```{r pop_dist, fig.cap = "Conditional distributions in the popularity data", echo=FALSE, message=FALSE, warning=FALSE}
# popmis %>% 
#   filter(as.numeric(school) < 5) %>% 
#   ggplot(aes(x = teachpop, color = school)) +
#     geom_density() +
#     facet_wrap(~factor(is.na(popular), labels = c("popular missing", "popular observed")), ncol = 1) +
#     # scale_color_manual(values = plot_col, name = "popular") +
#     theme_classic() # +
#     # theme(legend.position = "bottom")

plot_conditional(popmis, x = "texp", z = "popular", cluster = "school")
# TODO: check if up-side-down plot works
# TODO: check smoothing in geom_density function and make it the inverse of the sample size
# TODO: add functions to mice
# TODO: add title and informative legend
# TODO: add facets for some clusters
# or add propensity score distribution `is.na(popular) ~ .`
# TODO: make it average of cluster dens, not marginal
# alternatively add a quartile line around the density with geom_ribbon

## comments 24/1
# pop obs and pop miss in legend
# add to caption
# add fill
# overlap coeff??
# make densities proportional

@@

The first imputation model that we'll use is likely to be invalid. In this model, we ignore the multilevel structure of the data, despite the high ICCs. This is purely to illustrate the effects of ignoring the clustering in our imputation effort.

@@

#TODO: think about interactive clusters for the strippplots
#TODO: switch off outliers in boxplot?
```

@@

Add: Assumes exchangability between units.

@@

Schafer book fortran workflows.

@@

The data is already imputed (Steyerberg et al, 2008), so we'll induce missingness ourselves. For example, MAR missingness varying by cluster.^[Observed data pattern should differ per cluster. So, in cluster 1, the missingness would depend on age, but not in cluster two. Split the dataframe and run `ampute()` on each cluster.]

```{r impact, echo=FALSE, fig.width=5}
# load data
data("impact", package = "metamisc")
impact_NA <- readRDS("../Data/impact_NA.RDS")
# # descriptive statistics
# by(impact, impact$name, summary) 
# psych::describe(impact)[,c(2:5,8:9)]
# # missingness
plot_md_pat(impact_NA)

# md pattern in first cluster
plot_md_pat(impact_NA[impact_NA$name == "TINT", ])
plot_md_pat(impact_NA[impact_NA$name == "APOE", ])
# TODO: rotate variable labels

# TODO: check md pattern in clusters, should differ, otherwise create new missingness
# MAYBE: think about nr of clusters: if there's too many, faceting is no option -> some distribution across the clusters instead
# TODO: e-mail Joop for DGM or look at adrew and jennifer book for data
# sim.multi from psych
```

TODO: Look at analysis model, maybe copy from GREAT data example e.g., adjusted prognostic effect of ct on unfortunate outcomes. Add something about systematically missing data here. In the md pattern plot: rotate labels, make missingness % gradient for clusters (ie the number of clusters for which this variable is missing).

>>>>

---
documentclass: jss
author:
  - name: Hanne Oberman
    affiliation: Utrecht University
    address: |
      | Padualaan 14
      | 3584 CH Utrecht
    email: \email{h.i.oberman@uu.nl}
    url: https://hanneoberman.github.io/
  - name: Johanna Mu\~noz Avila
    affiliation: University Medical Center Utrecht \AND
  - name: Valentijn de Jong
    affiliation: University Medical Center Utrecht 
  - name: Gerko Vink
    affiliation: Utrecht University \AND
  - name: Thomas Debray
    affiliation: University Medical Center Utrecht 
title:
  formatted: "Imputation of Incomplete Multilevel Data with \\pkg{mice}"
  plain:     "Imputation of Incomplete Multilevel Data with mice"
  short:     "Multilevel \\pkg{mice}"
abstract: >
  This is a tutorial paper on imputing incomplete multilevel data with \pkg{mice}. Footnotes in the current version show work in progress/under construction. The last section is not part of the manuscript, but purely for reminders.
keywords:
  # at least one keyword must be supplied
  formatted: [missing data, multilevel, clustering, "\\pkg{mice}", "\\proglang{R}"]
  plain:     [missing data, multilevel, clustering, mice, R]
preamble: >
  \usepackage{amsmath}
header-includes: 
 - \usepackage{graphicx} 
 - \usepackage{mathtools}
 - \usepackage{ulem}
output: 
    rticles::jss_article: default
    word_document: default
bibliography: ../References/multilevelmice.bib
editor_options: 
  chunk_output_type: inline
---

@@

```{r patterns, fig.height=3, fig.width=4.1, fig.cap = "Missingness in multilevel data", echo=FALSE}
plot_md_set()
```

@@

Ignoring the missingness in analyses can be extremely harmful to inferences. Complete case analysis can introduce bias in statistical inferences and lowers statistical power. Instead, the missingness should be accommodated \emph{before} or _within_ the analysis of scientific interest. Especially the former is very generic and popular. Imputing (i.e., filling in) the missing values separates the missing data problem from the scientific problem: missing data are replaced by plausible values whereafter the completed data is analyzed as if it were completely observed. The \proglang{R} package \pkg{mice} has become the de-facto standard for imputation by chained equations, which iteratively solves the missingness on a variable-by-variable basis. \pkg{mice} is known to yield valid inferences under many different missing data circumstances [@buur18]. In this paper, we will discuss how to use \pkg{mice} in the context of multilevel data.

<!-- Another characteristic of the missing data to take into account in analyses is the mechanism behind the missingness. Although the essence of the true non-response mechanism may not be known, it can be inferred or assumed to be one of the following: -->
<!-- - Missing Completely At Random (MCAR), where the probability to be missing is equal across all data entries; -->
<!-- - Missing At Random (MAR), where the probability to be missing depends on observed information; -->
<!-- - Missing Not At Random (MNAR), where the probability to be missing depends on unrecorded information, making the missingness non-ignorable [@rubi76; @meng94]. -->
<!-- Depending on the assumed missingness mechanism, missing data handling strategies may be more or less suitable, see e.g., @yuce08 and @hox15. -->
<!-- "We find it useful to distinguish the missingness pattern, which describes which values are missing and observed in the data matrix and the missingness mechanism (or mechanisms), which concerns the relationship between missingness and the values of variables in the data matrix" (Little and Rubin, p. 8). -->

@@

For each of these datasets, we will discuss the nature of the missingness, choose one or more imputation models and evaluate the imputed data, but we will also highlight one specific aspect of the imputation workflow. With the `popmis` data, we show how (not) to develop an imputation model. With the `hiv` data we focus on extending the imputation model to include Heckman-type selection-inclusion methods. And with the `impact` data we provide an example of multivariate missingness in real-world data. Together, this should give enough scaffolding for applied researchers who are faced with incomplete multilevel data.

@@

```{r pop, echo=FALSE, message=FALSE, warning=FALSE}
# estimates complete popularity data
est_comp <- lme4::lmer(popular ~ 1 + sex + texp + sex:texp + (1 + sex | school), popcomp) 
# fixed effects only
est_comp_fixed <- est_comp %>% 
  broom.mixed::tidy("fixed", conf.int = TRUE) %>% 
  mutate(term = term,
         estimate  = paste0(
           round3(estimate), " [", 
           round3(conf.low), ", ", 
           round3(conf.high), "]"), 
         .keep = "none") %>% 
  as.data.frame()
# # random effects
# est_comp %>% 
#   broom.mixed::tidy("ran_pars") %>% 
#   mutate(term = term, #factor(term, levels = unique(.$term), labels = c()),
#          estimate  = round3(estimate), 
#          .keep = "none")
# # rename broom.mixed estimates
# lvl = c("(Intercept)", "sex", "texp", "sex:texp", "sd__(Intercept)", "cor__(Intercept).sex", "sd__sex", "sd__Observation")
# lbl = c("Intercept", "Sex", "Teacher experience", "Cross-level interaction", "SD cluster-level residual error", "Cor. cluster-level error and slopes sex", "SD residual slopes sex", "SD unit-level residual error")

# compare complete data to missingness
# popcomp <- popcomp %>% 
#   cbind(R = is.na(popmis$popular))
# t.test(x = popcomp$popular[popcomp$R], y = popcomp$popular[!popcomp$R]) 
# ggplot(popcomp, aes(y=popular, x = R)) +
#   geom_boxplot()
```

@@

@@

```{r comp_est, echo=FALSE}
est_comp_fixed %>% setNames(c("", "Estimate with 95% CI"))
```

@@

```{r pop_pat, echo=FALSE, fig.cap = "Missing data pattern in the popularity data", message=FALSE, warning=FALSE}
# missingness
plot_md_pat(popmis)
```

@@

In Figure \ref{fig:pop_dist} we see that **[update this part]** the distribution for the missing `popular` is further to the right than the distribution for observed `popular`. This would indicate a right-tailed MAR missingness. (In fact, this is exactly what happens, because the missingness in these data was created manually.) We've made it observable by examining the relations between the missingness in popular and the observed data in `texp`.

```{r pop_dist, fig.cap = "Conditional distributions in the popularity data", echo=FALSE, message=FALSE, warning=FALSE}
plot_conditional(popmis, x = "texp", z = "popular", cluster = "school")
# TODO: check if up-side-down plot works
# TODO: check smoothing in geom_density function and make it the inverse of the sample size
# TODO: add functions to mice
# TODO: add title and informative legend (pop obs and pop miss)
# TODO: add facets for some clusters, or add propensity score distribution `is.na(popular) ~ .`
# TODO: make it average of cluster dens, not marginal, alternatively add a quartile line around the density with geom_ribbon
# TODO: add fill and/or some way of expressing how much the densities overlap (overlap coefficient in %?)

# # maybe use facets instead
# popmis %>%
#   filter(as.numeric(school) < 5) %>%
#   ggplot(aes(x = texp, color = school)) +
#     geom_density() +
#     facet_wrap(~factor(is.na(popular), labels = c("popular missing", "popular observed")), ncol = 1) +
#     scale_color_manual(values = plot_col, name = "popular") +
#     theme_classic() # +
#     # theme(legend.position = "bottom")
```

@@

The first imputation model that we'll use is likely to be invalid. In this model, we ignore the multilevel structure of the data, despite the high ICCs. And assumes exchangeability between units. This is purely to illustrate the effects of ignoring the clustering in our imputation effort.

@@

#TODO: think about interactive clusters for the strippplots
```

@@

<!-- pmm: Single-level predictive mean matching with the school indicator coded as a dummy variable; -->
<!-- 2l.pan: Multilevel method using the linear mixed model to draw univariate imputations; -->
<!-- 2l.norm: Multilevel method using the linear mixed model with heterogeneous error variances; -->
<!-- 2l.pmm: Predictive mean matching based on predictions from the linear mixed model, with random draws from the regression coefficients and the random effects, using five donors. -->

@@

<!-- Look up Schafer book fortran workflows. -->

@@

The analysis model for this dataset is a prediction model with `mort` as the outcome.^[Look at analysis model, maybe copy from GREAT data example e.g., adjusted prognostic effect of ct on unfortunate outcomes. Add something about systematically missing data here.] The data is already imputed (Steyerberg et al, 2008), so we've induced missingness again based on the missingness in the original data.

```{r impact, echo=FALSE, fig.width=6, fig.height=8}
# load data
data("impact", package = "metamisc")
impact_NA <- readRDS("../Data/impact_NA.RDS")
# # descriptive statistics
# by(impact, impact$name, summary) 
# psych::describe(impact)[,c(2:5,8:9)]
# # missingness
plot_md_pat(impact_NA)
# TODO: rotate variable labels
# TODO: think about nr of clusters: if there's too many, faceting is no option -> some distribution across the clusters like shepley plot
# TODO: make missingness % gradient for clusters (ie the number of clusters for which this variable is missing).

```{r echo=FALSE}
# md pattern in first cluster
plot_md_pat(impact_NA[impact_NA$name == "TINT", ])
plot_md_pat(impact_NA[impact_NA$name == "APOE", ])
```

### 2022-02-11 Manuscript/Manuscript.tex
Clean-up and rename manuscript file

Ignoring the missingness in analyses can be extremely harmful to
inferences. Complete case analysis can introduce bias in statistical
inferences and lowers statistical power. Instead, the missingness should
be accommodated \emph{before} or \emph{within} the analysis of
scientific interest. Especially the former is very generic and popular.
Imputing (i.e., filling in) the missing values separates the missing
data problem from the scientific problem: missing data are replaced by
plausible values whereafter the completed data is analysed as if it were
completely observed. The \proglang{R} package \pkg{mice} has become the
de-facto standard for imputation by chained equations, which iteratively
solves the missingness on a variable-by-variable basis. \pkg{mice} is
known to yield valid inferences under many different missing data
circumstances \citep{buur18}. In this paper, we will discuss how to use
\pkg{mice} in the context of multilevel data.

@@

For each of these datasets, we will discuss the nature of the
missingness, choose one or more imputation models and evaluate the
imputed data, but we will also highlight one specific asect of the
imputation workflow. With the \texttt{popmis} data, we show how (not) to
develop an imputation model. With the \texttt{hiv} data we focus on
extending the imputation model to include Heckman-type
selection-inclusion methods. And with the \texttt{impact} data we
provide a example of multivariate missingness in real-world data.
Together, this should give enough scaffolding for applied researchers
who are faced with incomplete multilevel data.

@@

\begin{CodeChunk}
\begin{CodeOutput}
# A tibble: 4 x 2
  term        estimate                 
  <chr>       <chr>                    
1 (Intercept) " 3.314 [ 2.998,  3.629]"
2 sex         " 1.330 [ 1.069,  1.590]"
3 texp        " 0.110 [ 0.090,  0.130]"
4 sex:texp    "-0.034 [-0.051, -0.017]"
\end{CodeOutput}
\end{CodeChunk}

@@

Add: Assumes exchangability between units.

@@

Schafer book fortran workflows.

@@

The data is already imputed (Steyerberg et al, 2008), so we'll induce
missingness ourselves. For example, MAR missingness varying by
cluster.\footnote{Observed data pattern should differ per cluster. So,
  in cluster 1, the missingness would depend on age, but not in cluster
  two. Split the dataframe and run \texttt{ampute()} on each cluster.}

@@

\begin{center}\includegraphics{Manuscript_files/figure-latex/impact-2} \end{center}

\begin{center}\includegraphics{Manuscript_files/figure-latex/impact-3} \end{center}

@@

TODO: Look at analysis model, maybe copy from GREAT data example e.g.,
adjusted prognostic effect of ct on unfortunate outcomes. Add something
about systematically missing data here. In the md pattern plot: rotate
labels, make missingness \% gradient for clusters (ie the number of
clusters for which this variable is missing).

>>>>

Ignoring the missingness in analyses can be extremely harmful to
inferences. Complete case analysis can introduce bias in statistical
inferences and lowers statistical power. Instead, the missingness should
be accommodated \emph{before} or \emph{within} the analysis of
scientific interest. Especially the former is very generic and popular.
Imputing (i.e., filling in) the missing values separates the missing
data problem from the scientific problem: missing data are replaced by
plausible values whereafter the completed data is analyzed as if it were
completely observed. The \proglang{R} package \pkg{mice} has become the
de-facto standard for imputation by chained equations, which iteratively
solves the missingness on a variable-by-variable basis. \pkg{mice} is
known to yield valid inferences under many different missing data
circumstances \citep{buur18}. In this paper, we will discuss how to use
\pkg{mice} in the context of multilevel data.

@@

For each of these datasets, we will discuss the nature of the
missingness, choose one or more imputation models and evaluate the
imputed data, but we will also highlight one specific aspect of the
imputation workflow. With the \texttt{popmis} data, we show how (not) to
develop an imputation model. With the \texttt{hiv} data we focus on
extending the imputation model to include Heckman-type
selection-inclusion methods. And with the \texttt{impact} data we
provide an example of multivariate missingness in real-world data.
Together, this should give enough scaffolding for applied researchers
who are faced with incomplete multilevel data.

@@

\begin{CodeChunk}
\begin{CodeOutput}
                 Estimate with 95% CI
1 (Intercept)  3.314 [ 2.998,  3.629]
2         sex  1.330 [ 1.069,  1.590]
3        texp  0.110 [ 0.090,  0.130]
4    sex:texp -0.034 [-0.051, -0.017]
\end{CodeOutput}
\end{CodeChunk}

@@

@@

@@

The analysis model for this dataset is a prediction model with
\texttt{mort} as the outcome.\footnote{Look at analysis model, maybe
  copy from GREAT data example e.g., adjusted prognostic effect of ct on
  unfortunate outcomes. Add something about systematically missing data
  here.} The data is already imputed (Steyerberg et al, 2008), so we've
induced missingness again based on the missingness in the original data.

@@

@@

\begin{center}\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-1} \end{center}

\begin{center}\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-3-2} \end{center}
